FictionEro - Affective Impact of Fiction

### 2025-09-29 analysis/analysis.qmd
minor

>>>>

m_a1 <-  brms::brm(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (Relevance / Condition|Participant) + (1|Item),
                          data=df1, family=zero_one_inflated_beta())

# Enticement
m_e1 <-  brms::brm(Enticement ~ Gender /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
                          data=df1, family=zero_one_inflated_beta())

# Valence
m_v1 <-  brms::brm(Valence ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
                          data=df1, family=zero_one_inflated_beta())
```

m_a2<-  brms::brm(Arousal ~ Gender / Condition*ConditionBelief + (Condition|Participant) + (1|Item),
                          data=df2, family=zero_one_inflated_beta())
# Enticement
m_e2 <-  brms::brm(Enticing ~ Gender / Condition*ConditionBelief + (1|Participant) + (1|Item),
                          data=df2,family=zero_one_inflated_beta())
# Valence
m_v2 <-  brms::brm(Valence ~ Gender / Condition*ConditionBelief + (1|Participant) + (1|Item),
                          data=df2,family=zero_one_inflated_beta())
```
